---
title: "Get Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Setup
This is how you get REDCap turned into an R database...
```{r example, eval=FALSE}
library(REDCapSync)

projects <- get_projects()                         # get list of cached projects

View(projects)                             # show your previously saved projects
```
You can set your REDCap token in two ways! If you need more help setting your tokens see this article --> placeholder
```{r example2, eval=FALSE}
#1. set each time in your session (not recommended in saved/shared scripts!)
Sys.setenv(REDCapSync_TEST1 = "YoUrNevErShaReToken")
#2. set to your private R sessions!
usethis::edit_r_environ()                                       #finds your file
# Then you add --> REDCapSync_TEST = 'YoUrNevErShaReToken'
# then save file and restart R
# If it worked you will see your token when you run...
Sys.getenv("REDCapSync_TEST1")
```
## Run Core Functions
The following functions represent the core functions of the package.
```{r , eval=FALSE}
project <- setup_project(
  short_name = "TEST1",                #must match token pattern REDCapSync_**** 
  redcap_uri = "https://redcap.miami.edu/api/",  # change to your institutions link
  dir_path = getwd()                     # or change to your intended file path
)
project$sync() # gets all data from REDCap
```
## Explore Outputs!
```{r , eval=FALSE}
project$show_metadata(envir = globalenv())
project$generate_summary(
  summary_name = "REDCapSync_raw",
  envir = globalenv()
  ) 
```

## Go Further by Generating Summaries!

The following default merges all non-repeating forms and adds them to the right of any repeating forms. It also uses the REDCap log and REDCap data to add key information to metadata, users, and records.

```{r , eval=FALSE}
project$generate_summary(
  summary_name = "REDCapSync",
  envir = globalenv()
```

This can be customized with `add_summary` for refreshing datasets or `generate_summary` for R-only use. This can give you filtered data (and corresponding annotations to metadata, etc), de-identified data, and more!

```{r , eval=FALSE}
project$generate_summary(
    filter_field = "has_something" # Raw REDCap variable name
    filter_choices = "Yes"       # REDCap Labelled choice,
    exclude_identifiers = TRUE,
    exclude_free_text = TRUE,
    include_metadata = TRUE,
    envir = globalenv()
  )
```

